Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-20 idp/documents/documentation/paper.tex
froze date
added page breaks
fixed minor grammar error

\title{Optimal Fitting of Planar Curves to Prescribed Constraints}
\author{Julian Asamer, Julian Brunner}
\date{\today}

@@

				Applying the criteria established in section \ref{section:usability_criteria_curve_design_tools}, we conclude that the design tools for Bézier splines work sufficiently well in terms of humans trying to read and/or speak their specification language (criteria 2 and 3), a skill that can be acquired with some practice. The curve chosen by the fairness measure is also reasonably minimal (criterion 5), since the spline's complexity is limited by the number of segments that are used, which is in direct correspondence to the specification. Bézier splines are furthermore very simple to derive from their description, fulfilling criterion 6 perfectly. We think that design tools for Bézier splines have some issues with both the fairness measure's smoothness (criterion 4) and the expressiveness of the description language (criterion 1), both of which shall be analyzed in the following paragraphs.

>>>>

\title{Optimal Fitting of Planar Curves to Prescribed Constraints}
\author{Julian Asamer, Julian Brunner}
\date{February 13, 2014}

@@

				Applying the criteria established in section \ref{section:usability_criteria_curve_design_tools}, we conclude that the design tools for Bézier splines work sufficiently well in terms of humans trying to read and/or speak their specification language (criteria 2 and 3), a skill that can be acquired with some practice. The curve chosen by the fairness measure is also reasonably minimal (criterion 5), since the spline's complexity is limited by the number of segments that are used, which is in direct correspondence with the specification. Bézier splines are furthermore very simple to derive from their description, fulfilling criterion 6 perfectly. We think that design tools for Bézier splines have some issues with both the fairness measure's smoothness (criterion 4) and the expressiveness of the description language (criterion 1), both of which shall be analyzed in the following paragraphs.
